---
title: "Bioenergetics Model Inputs: Projected Climate Scenarios"
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r packages}
library(tidyverse)
library(readxl)
library(lubridate)
library(anytime)
library(janitor)
library(plotrix)
```

## Overview

This chapter generates FB4 input files for projected future climate scenarios. The approach mirrors Chapter 4 (observed inputs) with two key differences:

1. **Temperatures** come from downscaled projections rather than observed logger data
2. **Consumption (p-value)** is held fixed at mean, +20%, and −20% of the value estimated from 2015-2016 observed simulations, rather than being fit to a final weight

Three temperature scenarios × three consumption scenarios = nine model runs per cohort.

**Temperature scenarios:**

| Scenario | Period     | Description                          |
|----------|------------|--------------------------------------|
| Baseline | 2010-2019  | Near-present reference               |
| Near     | 2030-2039  | Mid-century                          |
| Far      | 2060-2069  | Late-century                         |

Each period is simulated under RCP 6.0 and RCP 8.5, giving six temperature × decade combinations.

All input files are committed to `other/FB4_1.1.3_projected.1/`. Code that writes to disk is marked `eval: false`.

---

## Projected Temperature Inputs

Projected air temperatures for each decade × RCP scenario were extracted from downscaled climate rasters at each field site and translated to projected water temperatures using linear air-water relationships derived from 2015-2016 field observations. Projections are available at monthly resolution.

```{r projected-temps}
projected_temps <- read.csv(
  "other/inputs/temperature/projected_temps.csv"
) |>
  select(-X, -proj_air_Temp_C, -sens_slope, -sens_int, -r_sq, -n_weeks) |>
  mutate(scenario = str_replace(scenario, "sres", "")) |>
  select(scenario, decade, month, Site, proj_h2o_Temp_C) |>
  rename(site = Site) |>
  group_by(scenario, decade, site, month) |>
  summarise(
    proj_dec_h2o_Temp = mean(proj_h2o_Temp_C),
    h2o_se = plotrix::std.error(proj_h2o_Temp_C, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(scenario_period = paste0(scenario, "_", decade))

glimpse(projected_temps)
```

The observed temperature data provides the date structure into which projected monthly means are joined. We substitute projected temperatures for observed temperatures.

```{r obs-temp-structure}
observed_temps <- read.csv(
  "other/inputs/temperature/observed_water_temp/daily_temp_metrics.csv"
) |>
  select(Stream_Name, Site, year, Date, doy, daily_avg_temp) |>
  rename(site = Site) |>
  mutate(
    year  = as.factor(year),
    Date  = as.Date(Date),
    month = month(Date)
  )

# Join projected temps to observed date structure (substituting projected for observed)
daily_proj_temps <- left_join(
  observed_temps,
  projected_temps,
  by = c("site", "month")
) |>
  select(scenario_period, Stream_Name, site, year, Date, doy,
         proj_dec_h2o_Temp) |>
  rename(daily_avg_temp = proj_dec_h2o_Temp)

glimpse(daily_proj_temps)
```

---

## Diet Proportion Inputs

The same wet-mass diet proportions from the observed chapter are used for all projected scenarios. Diet proportions do not change across climate scenarios — only temperature and consumption level change.

```{r diet-props}
wm_diet_props <- read.csv("other/outputs/diet/wet_mass_diet_proportions.csv")
wm_diet_props
```

---

## P-value Inputs from Observed Simulations

For projected simulations, we do not fit to a final weight. Instead, we hold the proportion of maximum consumption (p-value) fixed at the mean value estimated from 2015-2016 observed simulations, and also run at ±20% of that mean.

P-values are extracted from the committed FB4 output from Chapter 4.

```{r pvalue-inputs}
#| eval: false
# Requires committed FB4 output from the observed chapter
fb4_obs <- read.csv(
  "other/FB4_1.1.3_2015_2016.1/FB4_2015_2016_models_new_parameters.csv"
) |>
  clean_names() |>
  rename(Simulation = run_name) |>
  separate(Simulation,
           into = c("year", "season", "site", "spp", "e", "age"),
           sep  = "_", remove = FALSE) |>
  separate(site, into = c("reach", "river1", "river2"), remove = FALSE) |>
  mutate(Stream_Name = paste(river1, river2)) |>
  select(spp, age, year, season, site, reach, initial_w, p_value, Stream_Name)

# Projected simulation period: May 26 – September 4
min_sim_doy <- yday(ymd("2015-05-26"))
max_sim_doy <- yday(ymd("2015-09-04"))
sim_duration <- max_sim_doy - min_sim_doy

# Mean p-value by watershed × species × age
mean_pvals <- fb4_obs |>
  group_by(Stream_Name, spp, age) |>
  summarise(mean_pval = mean(p_value), .groups = "drop")

# Initial weight = mean weight at earliest sampling event per cohort
mean_start_w <- fb4_obs |>
  mutate(season_num = case_when(
    season == "Early Summer" ~ 1,
    season == "Mid-Summer"   ~ 2,
    season == "Late Summer"  ~ 3,
    season == "Fall"         ~ 4
  )) |>
  group_by(Stream_Name, spp, age, site) |>
  slice_min(season_num) |>
  summarise(mean_init_w = mean(initial_w), .groups = "drop")

# Build three consumption scenarios per cohort
init_file_dat <- left_join(mean_start_w, mean_pvals,
                           by = c("Stream_Name", "spp", "age")) |>
  mutate(
    `20plus_pval`  = mean_pval * 1.2,
    `20minus_pval` = mean_pval * 0.8
  ) |>
  pivot_longer(
    cols = c("mean_pval", "20plus_pval", "20minus_pval"),
    names_to  = "consumption_scenario",
    values_to = "value"
  ) |>
  mutate(Simulation = paste0(site, "_", spp, "_Age_", age))
```

---

## Simulation Temporal Extents

For projected scenarios, all cohorts share a common simulation window: **May 26 to September 4** (Julian days 146–247). This is the earliest date with weight data common across all sites and years, through the earliest final sampling visit plus 30 days.

Diet proportions are replicated across simulation days at the scale of river × species × age (no season grouping, unlike the observed simulations).

```{r proj-sim-days}
#| eval: false

# Temporal extent for projected simulations (one row per site × spp × age)
obs_diet_ref <- read.csv("other/outputs/observed_diet_proportions.csv") |>
  group_by(Stream_Name, site, spp, age) |>
  summarise(
    sim.start = as.integer(mean(yday(as.Date(sim.start)))),
    sim.end   = as.integer(mean(yday(as.Date(sim.end)))),
    .groups   = "drop"
  ) |>
  mutate(days = sim.end - sim.start)

diet_prop_proj <- left_join(wm_diet_props, obs_diet_ref,
                            by = c("Stream_Name", "spp", "age")) |>
  mutate(days = as.double(days))

sim_diet_days <- diet_prop_proj[
  rep(seq_len(nrow(diet_prop_proj)), diet_prop_proj[, "days"]), ] |>
  mutate(sim_name = paste0(site, "_", spp, "_Age_", age)) |>
  group_by(sim_name) |>
  mutate(
    SimDay = row_number(),
    doy    = sim.start + SimDay
  )

# Replicate for each scenario period
scenario_periods <- c(
  "rcp60_2030_2039", "rcp85_2030_2039",
  "rcp60_2060_2069", "rcp85_2060_2069",
  "rcp60_2010_2019", "rcp85_2010_2019"
)

sim_diet_days <- map_dfr(scenario_periods, function(sp) {
  sim_diet_days |> mutate(scenario_period = sp)
})

# Join monthly projected temperatures by month extracted from doy
sim_diet_days <- sim_diet_days |>
  mutate(
    date  = as.Date(doy, origin = as.Date("2015-01-01")),
    month = month(date)
  )

proj_temp_monthly <- daily_proj_temps |>
  filter(year == "2016") |>
  select(scenario_period, site, Stream_Name, month, daily_avg_temp) |>
  distinct()

sim_diet_days <- left_join(
  sim_diet_days, proj_temp_monthly,
  by = c("site", "scenario_period", "month", "Stream_Name")
) |>
  rename(avg_temp = daily_avg_temp) |>
  filter(!is.na(avg_temp)) |>
  rename(
    diet1 = FishEggs,
    diet2 = InvertAquatic_AqOrigin,
    diet3 = InvertTerrestrial,
    diet4 = InvertTerrestrial_AqOrigin,
    diet5 = SalmonEggs,
    Temp  = avg_temp
  ) |>
  mutate(diet6 = 0, diet7 = 0, diet8 = 0, diet9 = 0, diet10 = 0) |>
  select(-SimDay) |>
  group_by(sim_name, scenario_period, spp) |>
  mutate(SimDay = row_number()) |>
  ungroup() |>
  mutate(sim_name = paste0(scenario_period, "_", sim_name)) |>
  select(SimDay, Temp, diet1, diet2, diet3, diet4, diet5,
         diet6, diet7, diet8, diet9, diet10, sim_name, spp)

sim_diet_days[is.na(sim_diet_days)] <- 0
```

---

## Exporting Input Files

```{r export-proj-files}
#| eval: false

sim_filepath <- "other/FB4_1.1.3_projected.1/all_projected_sims"
unlink(sim_filepath, recursive = TRUE)
dir.create(sim_filepath, recursive = TRUE)

chnk_dir <- file.path(sim_filepath, "chnk", "")
coho_dir <- file.path(sim_filepath, "coho", "")
dir.create(chnk_dir, recursive = TRUE)
dir.create(coho_dir, recursive = TRUE)

export_proj_files <- function(sim_days, spp_filter, spp_dir) {
  df <- sim_days |> filter(spp == spp_filter) |> select(-spp)
  sim_names <- unique(df$sim_name)
  sim_subdirs <- file.path(spp_dir, sim_names)
  Map(dir.create, sim_subdirs, showWarnings = FALSE)

  for (nm in sim_names) {
    d <- file.path(spp_dir, nm)
    sub_df <- df |> filter(sim_name == nm) |> select(-sim_name)
    write.csv(sub_df |> select(SimDay, Temp) |> rename(day = SimDay, temperature = Temp),
              file.path(d, "Temperature.csv"), row.names = FALSE)
    write.csv(sub_df |> rename(day = SimDay),
              file.path(d, "Diet_prop.csv"), row.names = FALSE)
  }
}

export_proj_files(sim_diet_days, "Chinook", chnk_dir)
export_proj_files(sim_diet_days, "Coho",    coho_dir)

# Static inputs
day  <- c(1, 365)
dir_main <- "other/FB4_1.1.3_projected.1/projected_main_inputs/"
unlink(dir_main, recursive = TRUE)
dir.create(dir_main, recursive = TRUE)

Indigestible_Prey <- data.frame(
  day,
  diet1 = 0.03, diet2 = 0.17, diet3 = 0.17,
  diet4 = 0.17, diet5 = 0.03,
  diet6 = 0, diet7 = 0, diet8 = 0, diet9 = 0, diet10 = 0
)
write.csv(Indigestible_Prey, file.path(dir_main, "Indigestible_Prey.csv"),
          row.names = FALSE)

Pred_E <- data.frame(day, predator = 5000)
write.csv(Pred_E, file.path(dir_main, "Pred_E.csv"), row.names = FALSE)

Prey_E <- data.frame(
  day,
  diet1 = 5235, diet2 = 3365, diet3 = 5250,
  diet4 = 4225, diet5 = 9000,
  diet6 = 0, diet7 = 0, diet8 = 0, diet9 = 0, diet10 = 0
)
write.csv(Prey_E, file.path(dir_main, "Prey_E.csv"), row.names = FALSE)

copy_static <- function(src_dir, dest_spp_dir) {
  sims <- list.dirs(dest_spp_dir, recursive = FALSE)
  for (fname in c("Indigestible_Prey.csv", "Pred_E.csv", "Prey_E.csv")) {
    Map(file.copy,
        from = file.path(src_dir, fname),
        to   = file.path(sims, fname),
        overwrite = TRUE)
  }
}
copy_static(dir_main, chnk_dir)
copy_static(dir_main, coho_dir)
```

---

## Design File

```{r design-file-projected}
#| eval: false

folder_dirs <- bind_rows(
  as.data.frame(list.dirs(coho_dir)) |> setNames("dir"),
  as.data.frame(list.dirs(chnk_dir)) |> setNames("dir")
) |>
  clean_names() |>
  separate(dir, sep = "/", into = c("a","b","c","d","sim")) |>
  filter(!is.na(sim)) |>
  select(sim) |>
  rename(Simulation = sim)

build_design <- function(init_dat, folder_dirs, param_label) {
  design_colnames <- read.csv(
    "other/FB4_1.1.3_2015_2016.1/FB4_Design_Bluegill_1.csv"
  ) |> colnames()

  dat <- init_dat |>
    inner_join(folder_dirs, by = "Simulation") |>
    mutate(
      spp2 = ifelse(spp == "Coho", "coho", "chnk"),
      NRun        = row_number(),
      Run_Name    = paste0(consumption_scenario, "_", Simulation),
      Species_Num = ifelse(spp == "Coho", "22", "21"),
      Species_txt = ifelse(spp == "Coho",
                           "Coho salmon (adult)", "Chinook salmon (adult)"),
      Initial_W   = mean_init_w,
      fit.to      = "p-value",
      fit.to.value = value,
      First_day   = 1,
      Last_day    = sim_duration,
      N_indiv     = 1,
      Oxycal      = 13560,
      calc.pop_mort = "FALSE", calc.spawn = "FALSE",
      calc.nut = "FALSE", calc.contaminant = "FALSE",
      Init_pred_conc = "NA", contam_eq = "NA",
      T_File     = paste0("all_projected_sims/", spp2, "/", Simulation, "/Temperature.csv"),
      Diet_File  = paste0("all_projected_sims/", spp2, "/", Simulation, "/Diet_prop.csv"),
      Prey_E_File = paste0("all_projected_sims/", spp2, "/", Simulation, "/Prey_E.csv"),
      Indigest_Prey_File = paste0("all_projected_sims/", spp2, "/",
                                  Simulation, "/Indigestible_Prey.csv"),
      Pred_E_File = paste0("all_projected_sims/", spp2, "/", Simulation, "/Pred_E.csv"),
      Mort_File = "NA", Reprod_File = "NA",
      Contam_Prey_C_File = "NA", Contam_assim_File = "NA",
      Contam_TE_File = "NA",
      Phos_Ae_File = "NA", Phos_Co_Pred_File = "NA", Phos_Co_Prey_File = "NA",
      Nit_Ae_File = "NA", Nit_Co_Pred_File = "NA", Nit_Co_Prey_File = "NA",
      FB4_Log_File = "FB4_projected_models.csv",
      .keep = "unused"
    ) |>
    select(any_of(design_colnames))

  out_path <- paste0("other/FB4_1.1.3_projected.1/design_projected_",
                     param_label, ".csv")
  file.remove(out_path)
  write.csv(dat, out_path, row.names = FALSE)
  dat
}

# Run for both parameter sets (same design structure; FB4 uses different
# internal parameter files selected at run time)
design_new <- build_design(init_file_dat, folder_dirs, "new_parameters")
design_old <- build_design(init_file_dat, folder_dirs, "old_parameters")
```

---

## Running Fish Bioenergetics 4.0 (Projected Scenarios)

::: {.callout-note}
## Manual step: Running FB4 v1.1.3 for projected scenarios

1. Set the FB4 working directory to `other/FB4_1.1.3_projected.1/`
2. Load `design_projected_new_parameters.csv` (for Plumb & Moffitt parameters)
3. Run simulations; output written to `FB4_projected_models_new_parameters.csv`
4. Repeat with `design_projected_old_parameters.csv` (for Stewart & Ibarra parameters)

Both output files are committed and read in Chapter 6 (Simulation Results).

Note: the projected simulations fit to a fixed p-value rather than a final weight.
:::

---

## Committed FB4 Projected Outputs

```{r proj-outputs}
#| eval: false

proj_old <- read.csv(
  "other/FB4_1.1.3_projected.1/FB4_projected_models_old_parameters.csv"
)
proj_new <- read.csv(
  "other/FB4_1.1.3_projected.1/FB4_projected_models_new_parameters.csv"
)

glimpse(proj_old)
```
